---
title: "Untitled"
author: "Sydney Jansen"
date: "2024-03-25"
output: html_document
---
thoroughly describe and run the code for all of the steps in your reanalysis.

```{r setup, include=FALSE}
# These are some {knitr} options I typically use to format my **RMarkdown** documents in a consistent way. You should feel free to alter these or use other "chunk options" as you see fit!
# Sometimes, for example, you might want to suppress warnings or messages, and that behavior can be set for specific code chunks individually in the chunk header, e.g., ```{r warning = FALSE, echo = FALSE}
knitr::opts_chunk$set(
  eval = TRUE, # run code in code chunks
  echo = TRUE, # render output of code chunks
  warning = TRUE, # do not suppress "warnings"
  message = TRUE, # do not suppress "messages"
  comment = "##", # prefix for comment lines
  prompt = ">", # prefix for code lines
  tidy = TRUE,
  tidy.opts = list(blank = FALSE, width.cutoff = 75),
  fig.path = "images/", # name of folder for images
  fig.align = "center" # centers any images on the page
)
```

## Introduction
Objective: To investigate vocal plasticity in the tokay gecko (Gekko gecko) by determining if the geckos adjusted the properties of their calls in response to changes in background noise. {the first evidence for vocal plasticity in a reptile}

Methods: The researchers recorded advertisement calls of captive-bred male tokay geckos under different noise conditions and analyzed the duration and amplitude of different call types. 6 males were placed in a sound-chamber with opposing speakers: white noise encapsulating their hearing range and their calls recorded for 4 days. During the recording session, 24 h periods of broadcast noise were alternated with 24 h periods of silence.

Results: Geckos increased the duration of their call syllables in response to noise, but did not adjust the amplitude of their calls. Instead, they produced more high-amplitude syllables and fewer low-amplitude syllables in noise. This demonstrated that the geckos were able to increase the overall signal-to-noise ratio of their calls without using the Lombard effect. In other words, the geckos traded the number of low-amplitude and high-amplitude syllables in each call series to produce more of the louder notes in noise, rather than increasing the amplitude of all components of their call. 

What I intend to replicate: 

## Visualization of Data

[Include a view of the first few lines of the dataset plus any exploratory data analysis - e.g., overview of descriptive statistics included in the paper, plots, etc.]

## Statistical Replications/Reanalysis

[Be sure to **thoroughly** explain what replications you are doing and comment your code so that it is easy for a reader to understand. Include in this section relevant tables/figures/values from the original paper for comparison to what you accomplished with your replication. Note that I want you to do the bulk of any *exposition* using text and markdown syntax outside of code blocks. That is, your document should not just be one big code block with ***R*** style comments but rather a nicely formatted report with code separated from exposition, interpretation, and dicussion.]

## Summary/Discussion

[Narrative section that overviews how successful were you at replicating the analyses and visualizations in the study. What problems did you encounter? Why might you have encountered those problems? What details were lacking from the original study's methods that might have hampered your ability to replicate the authors' results?]

## References
Brumm H, Zollinger SA. 2017 Vocal plasticity in a reptile. Proc. R. Soc. B 284: 20170451.http://dx.doi.org/10.1098/rspb.2017.0451

[Include the citation for your paper, plus any other literature you might reference.]
Descriptive statistical analysis (summarizing and describing the primary properties of a dataset):

The effect of the treatment (noise/no noise) on amplitude, duration, and the  number of  call types  was examined  with separate models in R using the package lme4. In each model the individual and the call series were fitted as random effects to control for the repeated measures design. The treatment effects on amplitude and duration were investigated with linear mixed models(LMMs), model residuals were checked visually. 
```{}

```
Visualization statistical analysis (graphs):

The effect on the number of call types was examined with generalized linearmixed models (GLMMs), in which the count data were fitted with a Poisson distribution and a log link function. 

Figure 3: This figure shows the correlation between the two syllable types (cackles and GECK-O syllables) within tokay call series. ​ It includes two sub-figures: (a) a sample across five males with five randomly selected calls from each, and (b) all calls from the male from which the highest number of calls was recorded. ​ The size of the bubbles represents the number of observations.

```{r }

```
Inferential statistical analysis ( the practice of using sampled data to draw conclusions or make predictions about a larger sample data sample or population):

The relationship between the number of cackle calls and the number of GECK-O syllables in a call series was investigated with Spearman rank correlations (using SPSS Statistics 21). This was done with two data sets: (i) across all males that produced at least five call series, from each of these (n¼5 males) we randomly selected five call series independent of the treatment,and (ii) within the one male from which we recorded the highest number of calls (n¼254 calls)


The authors performed several inferential statistical analyses in their study. Specifically, they used linear mixed models (LMMs) and generalized linear mixed models (GLMMs) to examine the effects of the noise treatment on various call parameters, such as amplitude, duration, and the number of call types. ​ They also used likelihood ratio tests to compare models including the treatment to null models. 


```{r }

```

```{r }

```
